---
title: "Stroke Risk Descriptive Graphical Report"
author: Michela Stephens
output:
  html_document:
    font adjustment: +2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction


<p style="font-family: times, serif; font-size:12pt">
This dataset contains information collected from a clinical trial of stroke risk. It contains a total of 5110 patients who were followed for a ten-year interval. Information collected includes gender, age, hypertension, heart disease, residence type, average blood glucose level, BMI, and smoking status. This report shows a graphical analysis of the dataset. 
</p>



### Loading Data

```{r, read-data, warning = FALSE, message = FALSE}
here::i_am("StrokeReport_Graphical.Rmd")
stroke_data <- read.csv(here::here("Data/healthcare-dataset-stroke-data.csv"))
```


### Descriptive Analysis - Bar Graph of Smoking Status

```{r, figure-one, echo = FALSE}
#| fig.align = "center",
#| out.width = "800px"

readRDS(file = here::here("output/bar_graph.rds"))
```

<br>



<p style="font-family: times, serif; font-size:12pt">
The graph above shows the counts for smoking status among the study participants. The most common category was never smoker and the least common category was current smoker. There are a large count of individuals with unknown smoking status, which may cause problems in an exploratory analysis.
</p>


<br>

### Logisitic Regression Model

```{r, plot-data}
#| fig.align = "center",
#| out.width = "800px"
readRDS(
  file = here::here("output/regression_mod.rds")
)

```
<br>



<p style="font-family: times, serif; font-size:12pt">
The graph above shows the graphical representation for the logistic regression model. It shows a significant association between average glucose level and risk for stroke. 
</p>


<br>

